### 2018-05-31 HSF-TN/draft-2015-NAM/draft-HSF-TN-2015-NAM.tex
update naming conventions w/ feedback from Graeme

% Abstract -----------------------------------------------
\begin{abstract}
  \noindent
  The note describes a proposal for a common platform naming scheme for HEP and tools to automatize the platform identification. 
\end{abstract}

@@

In the view of the fact, that naming conventions are just agreements we propose to adopt existing naming conventions wherever possible and useful.

@@

Different OSes may call the same \emph{architecture} with different names. We propose to rely on the abstraction of the Python package \emph{platform}, namely \texttt{platform.machine()}. This translates to e.g. x86\_64 for current Intel and AMD CPUs. In cases where optimized builds for a certain processor generation are required and software is not runable on the generic architecture, the generic architecture should be replaced by \emph{architecture+instructionset}. 
There exist no stable conventions for the instruction set, thus we propose to create ad-hoc conventions.

@@

\subsection{Compiler}
The \emph{compiler} is a combination of compiler name and compiler version. We propose to use the self-given names of the compilers like \emph{gcc, clang, msvc, icc} and adding major, minor version, and patch version numbers to it, e.g. \emph{clang350} or \emph{gcc511}. In case the system compiler is being used, the compiler should be denoted as \emph{native}.

\subsection{Buildtype}
The \emph{buildtype} denotes whether there is a debug build, an optimized build, or any other special setting. We propose to use \emph{opt} for optimized and \emph{dbg} for debug builds. The buildtype can be used to specify further custom build options, e.g. the used C++ standard, leading to opt11 or dbg14.
In general, any special compile time setting can be tracked in this name component.

@@

\section{Identification tool -- hsf\_get\_platform}
As to simplify the adoption of these conventions, we provide a minimal command line tool \emph{hsf\_get\_platform}, that is able to identify architecture, operating system, and compiler in a transparent way. It can be used to e.g. auto-derive everything in a given environment or to extract one part of the platform string
\\
\texttt{hsf\_get\_platform.py --buildtype opt $\rightarrow$ "x86\_64-ubuntu15-gcc49-opt"}
\\
\texttt{hsf\_get\_platform.py --get compiler $\rightarrow$ "gcc49"}.

>>>>

% Abstract -----------------------------------------------
\begin{abstract}
  \noindent
  The note describes a proposal for a common platform naming scheme for HEP and tools to automate the platform identification.
\end{abstract}

@@

In the view of the fact that naming conventions are just agreements we propose to adopt existing naming conventions wherever possible and useful.

@@

Different OSes may call the same \emph{architecture} by different names. We propose to rely on the abstraction of the Python package \emph{platform}, namely \texttt{platform.machine()}. This translates to, e.g., x86\_64 for current Intel and AMD CPUs. In cases where optimized builds for a certain processor generation are required and software is not runable on the generic architecture, the generic architecture should be replaced by \emph{architecture+instructionset1+instructionset2...}. For example \emph{x86\_64+avx2} denotes an x86\_64 processor supporting the AVX2 instruction set.
There exist no explicit conventions for the instruction set across operating systems, thus we propose to create ad-hoc conventions. In the Linux case the \emph{flags} field of \emph{/proc/cpuinfo} could be used. The instruction sets mentioned should be ordered alphabetically to ensure consistency.

@@

\subsection{Compiler}
The \emph{compiler} is a combination of compiler name and compiler version. We propose to use the self-given names of the compilers like \emph{gcc, clang, msvc, icc} and adding the compiler version indicating feature relevant versions. That can be major, minor version, and patch version numbers for LLVM (e.g. \emph{clang350}) or just major and minor version for GCC (e.g. \emph{gcc73}). In case the system compiler is being used, the compiler should be denoted as \emph{native}.

\subsection{Buildtype}
The \emph{buildtype} denotes whether there is a debug build, an optimized build, or any other special setting. We propose to use \emph{opt} for `optimized` and \emph{dbg} for debugging builds. The buildtype can be used to specify further custom build options, e.g. the used C++ standard, leading to \emph{opt+std14} or \emph{dbg+std18}.
In general, any special compile time setting can be tracked in this name component.

@@

\section{Identification tool -- hsf\_get\_platform}
As to simplify the adoption of these conventions, we provide a minimal command line tool \emph{hsf\_get\_platform}, that is able to identify architecture, operating system, and compiler in a transparent way. It can be used to, e.g., auto-derive everything in a given environment or to extract one part of the platform string
\\
\texttt{hsf\_get\_platform.py --buildtype opt $\rightarrow$ "x86\_64-ubuntu15-gcc49-opt"}
\\
\texttt{hsf\_get\_platform.py --get compiler $\rightarrow$ "gcc49"}.
